Learning CNN filters from user-drawn image markers for coconut-tree image classification

### 2020-07-23 main.tex
pipeline to train classifier

    \end{tikzpicture}
  \end{center}
  \caption{Pipeline.}
  \label{fig:pipeline}
\end{figure*}

\begin{comment}

@@

    \tikzstyle{steps} = [rectangle, rounded corners, minimum width=1.3cm, minimum height=0.7cm,text centered, draw=black,fill=violet!30, execute at begin node={\begin{varwidth}{2.5cm}},
    execute at end node={\end{varwidth}}]
    \tikzstyle{image} = [minimum width=1.3cm, minimum height=0.7cm,text centered, draw=white,fill=white!30, inner sep=0pt]

@@

     \node (imgs) [fit={($(img1.north west)+(-0.45,0.2)$) ($(img3.south east)+(0.45,-0.2)$)}, inner sep=0pt, draw=none, rounded corners, very thick, label = {[label distance = 0.3em]below:{Images}}] {};
     %----------------------------------

     \node (vis1) [image, right=1.5em of tsne, outer sep=0pt] {\includegraphics[width=.12\textwidth]{figures/input_200.png}};

     \node (select) [steps, right=1.35em of vis1] {Select Images};

    %images----------------------------
    \node (simg1) [image, above right=-2em and 3em of select] {\includegraphics[width=.08\textwidth]{figures/img1.png}};
    \node (simg2) [image, below left=-5em of simg1] {\includegraphics[width=.08\textwidth]{figures/img2.png}};
    \node (simg3) [image, below left=-5em of simg2] {\includegraphics[width=.08\textwidth]{figures/img3.png}};
    \node (simg4) [image, below left=-5em of simg3] {\includegraphics[width=.08\textwidth]{figures/img4.png}};

    \node (simgs) [fit={($(simg1.north west)+(-0.64,0.2)$) ($(simg4.south east)+(0.64,-0.2)$)}, inner sep=0pt, draw=none] {};
    %----------------------------------

     \node (put) [steps, right=1em of simgs] {Put Markers};

     %images----------------------------
    \node (mimg1) [image, above right=-2em and 3em of put] {\includegraphics[width=.08\textwidth]{figures/markers1.png}};
    \node (mimg2) [image, below left=-5em of mimg1] {\includegraphics[width=.08\textwidth]{figures/markers2.png}};
    \node (mimg3) [image, below left=-5em of mimg2] {\includegraphics[width=.08\textwidth]{figures/markers3.png}};
    \node (mimg4) [image, below left=-5em of mimg3] {\includegraphics[width=.08\textwidth]{figures/markers4.png}};

    \node (mimgs) [fit={($(mimg1.north west)+(-0.64,0.2)$) ($(mimg4.south east)+(0.64,-0.2)$)}, inner sep=0pt, draw=none] {};
    %----------------------------------

     \node (flim) [steps, below left=5em and -3em of mimgs] {FLIM};

     \node (ft) [steps, left=2em of flim] {Feature Extractor};

     \node (aft) [steps, left=2em of ft] {Apply Featute \\ Extractor};

      %images----------------------------
    \node (f1) [image, above left=-2.8em and 2em of aft] {\includegraphics[width=.07\textwidth]{figures/features/f1.png}};
    \node (f2) [image, below left=-5em of f1] {\includegraphics[width=.07\textwidth]{figures/features/f2.png}};
    \node (f3) [image, below left=-5em of f2] {\includegraphics[width=.07\textwidth]{figures/features/f3.png}};
    \node (f4) [image, below left=-5em of f3] {\includegraphics[width=.07\textwidth]{figures/features/f4.png}};

    \node (features) [fit={($(f1.north west)+(-0.17,0.2)$) ($(f4.south east)+(0.17,-0.2)$)}, draw=none, inner sep=0pt] {};
    %----------------------------------

     \node (clf) [steps, left=2em of features] {Train classifier};

     %--------------------------------------------------------------arrows
     \draw [arrow, myarrow] (imgs) -- (tsne);
     \draw [arrow, myarrow] (tsne) -- (vis1);
     \draw [arrow, myarrow] (vis1) -- (select);
     \draw [arrow, myarrow] (select) -- (simgs);
     \draw [arrow, myarrow] (simgs) -- (put);
     \draw [arrow, myarrow] (put) -- (mimgs);
     \draw [arrow, myarrow] (mimgs) -- (flim);
     \draw [arrow, myarrow] (flim) -- (ft);
     \draw [arrow, myarrow] (ft) -- (aft);
     \draw [arrow, myarrow] (aft) -- (features);
     \draw [arrow, myarrow] (features) -- (clf);
     \draw [arrow, myarrow] (imgs) -- (aft);

    \end{tikzpicture}
  \end{center}
  \caption{Pipeline.}
  \label{fig:pipeline}
\end{figure*}
\end{comment}

>>>>

    \end{tikzpicture}
  \end{center}
  \caption{Pipeline to trian a feature extractor.}
  \label{fig:pipeline-xtractor}
\end{figure*}

@@

@@

    \begin{tikzpicture}[node distance=1.5cm]

      %images----------------------------
     \node (img1) [image] {\includegraphics[width=.08\textwidth]{figures/qualitative/ours/lower-coco-789.png}};
     \node (img2) [image, below left=-5em of img1] {\includegraphics[width=.08\textwidth]{figures/qualitative/ours/lower-coco-789.png}};
     \node (img3) [image, below left=-5em of img2] {\includegraphics[width=.08\textwidth]{figures/qualitative/ours/lower-coco-789.png}};

     \node (aft) [steps, right=2em of imgs] {Apply Featute\\Extractor};

      %images----------------------------
    \node (f1) [image, above right=-3em and 3em of aft] {\includegraphics[width=.08\textwidth]{figures/features/f1.png}};
    \node (f2) [image, below left=-5.5em of f1] {\includegraphics[width=.08\textwidth]{figures/features/f2.png}};
    \node (f3) [image, below left=-5.5em of f2] {\includegraphics[width=.08\textwidth]{figures/features/f3.png}};
    \node (f4) [image, below left=-5.5em of f3] {\includegraphics[width=.08\textwidth]{figures/features/f4.png}};

    \node (features) [fit={($(f1.north west)+(-0.3,0.2)$) ($(f4.south east)+(0.3,-0.2)$)}, draw=none, inner sep=0pt, label = {[label distance = 0.1em]below:{Features}}] {};
    %----------------------------------

     \node (sup) [steps, right=2em of features] {Supervised\\Learning};

     \node (clf) [steps, right=2em of sup] {Classifier};

     %--------------------------------------------------------------arrows

     \draw [arrow, myarrow] (imgs) -- (aft);
     \draw [arrow, myarrow] (aft) -- (features);
     \draw [arrow, myarrow] (features) -- (sup);
     \draw [arrow, myarrow] (sup) -- (clf);

    \end{tikzpicture}
  \end{center}
  \caption{Pipeline to train a classifier.}
  \label{fig:pipeline-classifier}
\end{figure*}
